---
title: "Bootstrapping"
author: "Brooklynn McNeil"
date: "2024-11-14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(p8105.datasets)
library(purrr)
```

## Class Notes

Repeated Sampling
-   it would be great if we could draw multiple samples from the same population, but that never really happens
-   what we end up doing is splitting our sample into multiple samples

Bootstrapping
-   your sample is drawn at random from the population
-   draw a sample with replacement

Why Bootstrapping?
-   we want to prove that all of our assumptions are met in order to use the "known" distribution

## Boostrapping!

let's make up some data

```{r}
n_samp = 250

sim_df_constant = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconstant = 
  sim_df_constant |>
  mutate(
    error = error * 0.75 * x,
    y = 2 + 3 * x + error
  )
```

Let's look at these.

```{r}
sim_df_constant |>
  ggplot(aes(x = x, y =y)) +
  geom_point() +
  stat_smooth(method = "lm")

sim_df_nonconstant |>
  ggplot(aes(x = x, y =y)) +
  geom_point() +
  stat_smooth(method = "lm")
```

Look at regression results.

```{r}
sim_df_constant |>
  lm(y ~ x, data = _) |>
  broom::tidy() |>
  knitr::kable(digits = 3)

sim_df_nonconstant |>
  lm(y ~ x, data = _) |>
  broom::tidy() |>
  knitr::kable(digits = 3)
```

## Draw a bootstrap sample

```{r}
boot_samp = function(df) {
  
  boot_df = sample_frac(df, replace = TRUE) |>
    arrange(x)
  
  return(boot_df)
  
}
```

Let's run it!

```{r}
sim_df_nonconstant |>
  boot_samp() |>
  ggplot(aes(x =x, y =y)) +
  geom_point(alpha = 0.5) +
  stat_smooth(method = "lm")
```

Can we do this as part of an anlaysis. 

```{r}
sim_df_nonconstant |>
  boot_samp() |>
  lm(y ~ x, data = _) |>
  broom::tidy() |>
  knitr::kable(digits = 3)
```

## Boostrap A LOT

```{r}
boot_straps = 
  tibble(
    strap_n = 1:1000
    ) |>
  mutate(
    strap_samp = map(strap_n, \(i) boot_samp(df = sim_df_nonconstant)),
    models = map(strap_samp, \(df) lm(y ~ x, data = df)),
    results = map(models, broom::tidy)
    )

boot_strap_results =
  boot_straps |>
  select(strap_n, results) |>
  unnest(results) |>
  group_by(term) |>
  summarize(boot_se = sd(estimate)) |>
  knitr::kable()
```

## do all this using modelr

```{r}
boot_straps = 
  sim_df_nonconstant |>
  modelr::bootstrap(1000) |>
  mutate(
    strap = map(strap, as.tibble),
    models = map(strap, \(df) lm(y ~ x , data = df)),
    results = map(models, broom::tidy)
  ) |>
  select(.id, results) |>
  unnest(results)
```

## Air bnb data

```{r}
data("nyc_airbnb")

manhattan_df = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough == "Manhattan") |> 
  drop_na(price, stars) |> 
  select(price, stars, room_type)
```

Plot the data

```{r}
manhattan_df |>
  ggplot(aes(x = stars, y = price)) +
  geom_point() +
  stat_smooth(method = "lm", se = FALSE)
```

fit a regression

```{r}
manhattan_df |>
  modelr::bootstrap(1000) |>
  mutate(
    strap = map(strap, as.tibble),
    models = map(strap, \(df) lm(price ~ stars + room_type, data = df)),
    results = map(models, broom::tidy)
    ) |>
  select(.id, results) |>
  unnest(results) |>
  filter(term == "stars") |>
  ggplot(aes(x = estimate)) +
  geom_density()
```

